---
title: "Analysing R-universe"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Analysing R-universe}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(woodendesc)
```

R-universe is a platform by rOpenSci that provides an alternative way of creating package ecosystems. It tracks specified packages on GitHub/GitLab and creates a "universe" containing packages, builds, vignettes, accessible API... That's why we opened [our own turtleverse](https://turtletopia.r-universe.dev/packages).

## Packages

Each universe has separate package list, so the user should specify the relevant universe through the `universe` parameter.

```{r packages, cache=TRUE}
wood_runiverse_packages(universe = "turtletopia")
```

## Available package version

Since R-universe works by pointing to the latest commit on the main branch, there's always one version of a package; to extract it the user should use `wood_runiverse_version()`.

```{r version, cache=TRUE}
wood_runiverse_version("gglgbtq", universe = "turtletopia")
```

## Package dependencies

R-universe API is actually nice enough to return dependency data, but they still have to be parsed before returning.

```{r deps, cache=TRUE}
wood_runiverse_dependencies("gglgbtq", universe = "turtletopia")
```
