---
title: "Analysing any URL"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Analysing any URL}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(woodendesc)
```

Other than all the explicitly supported repositories (CRAN, Bioconductor, etc.), locally set up repositories can also be analysed using {woodendesc}. The requirement is they must contain the `PACKAGES` file (or `PACKAGES.gz`, its compressed counterpart) under `/src/contrib` path; the file should effectively be a concatenation of relevant attributes from all `DESCRIPTION` files of the packages the repository contains.

## Packages

To list all available packages the user should use `wood_url_packages()`.

```{r packages, cache=TRUE}
wood_url_packages("https://colinfay.me")
```

## Available package version

The structure of `PACKAGES` file allows only one version to be stored, so `wood_url_version()` may only return this one version.

```{r version, cache=TRUE}
wood_url_version("dockerfiler", repository = "https://colinfay.me")
```

## Package dependencies

The `PACKAGES` file is supposed to contain dependency data as well.

```{r deps, cache=TRUE}
wood_url_dependencies("tidystringdist", repository = "https://colinfay.me")
```
